% This is the aspauthor.tex LaTeX file
% Copyright 2010, Astronomical Society of the Pacific Conference Series

\documentclass[11pt,twoside]{article}
\usepackage{asp2010}

\resetcounters

\bibliographystyle{asp2010}

\markboth{Bell et al.}{A New Archive of UKIRT Legacy Data at CADC}

\begin{document}

\title{A New Archive of UKIRT Legacy Data at CADC}
\author{Graham~S.~Bell,$^1$ Malcolm~J.~Currie,$^1$ Russell~O.~Redman,$^2$ Maren~Purves,$^1$ and Tim~Jenness$^{1,3}$
\affil{$^1$Joint~Astronomy~Centre, 660~N.~A`oh\={o}k\={u}~Place, Hilo, HI, 96720, U.S.A.}
\affil{$^2$Canadian Astronomy Data Centre, 5071 West Saanich Road, Victoria, BC, V9E 2M7, Canada}
\affil{$^3$Department of Astronomy, Cornell University, Ithaca, NY, 14853, U.S.A.}}

\begin{abstract}
A new archive of raw data from the United Kingdom Infrared
Telescope (UKIRT) is being constructed at the Canadian Astronomy
Data Centre (CADC).  It contains all data available apart from
that from the Wide Field Camera (WFCAM), which is already
accessible from the WFCAM Science Archive.

The desire was to archive the data in as close to its original raw
format as possible.  Where the data followed our current convention
of having a single data file per observation, it was archived
without alteration, except for minor fixes to headers of data in
FITS format to allow it to pass fitsverify and be accepted by CADC.
Some of the older data comprised multiple integrations in separate
files per observation, stored in either NDF or DST format. These
were placed inside HDS container files, and DST files were rearranged
into NDF format.

The process of ingesting the metadata into the CAOM-2 repository
was broken into two stages.  First the headers were read from
the data files and stored in an intermediate MongoDB database.
Then the ingestion process uses this database to generate an XML
file for each observation and sends this file to the repository.

The final stage is to run the ORAC-DR pipeline to generate reduced
data products.  The intermediate database can be used to identify
groups of observations to be processed together and to supply
additional data where the original headers were insufficient.
\end{abstract}

\section{Introduction}

\ldots

CAOM-2 \citep{2012ASPC..461..339D}

WSA \citep{2008MNRAS.384..637H}

\section{Transfer of Data to CADC}

Electronic Transfer \citep{2005ASPC..347..647M}

NDF \citep{P91_adassxxiii}

\ldots

\section{Ingestion of Metadata into CAOM-2}

\ldots

\section{Data Reduction Pipeline}

ORAC-DR \citep{1999ASPC..172...11E,2008AN....329..295C}

HdrTrans \citep[section 2.2]{2008AN....329..295C}

JSA \citep{2011ASPC..442..203E}

\ldots

\section{Conclusions}

\ldots

\bibliography{P01}

\end{document}
